---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## Observation of Local cars and their types and colours


```{r}
library(tidyverse)

read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRujWLtqEWiSAHXUFE2tHAGrtY2dMZd8s52el1I9b6GdQ6PtF4erj5Q6fk3khWTiPXeSmLfTHayZfLf/pub?output=csv")

# Step 1: Read CSV data from URL into a data frame called logged_data
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRujWLtqEWiSAHXUFE2tHAGrtY2dMZd8s52el1I9b6GdQ6PtF4erj5Q6fk3khWTiPXeSmLfTHayZfLf/pub?output=csv")

# Check structure and column names of data
glimpse(logged_data)

latest_data <- logged_data %>%
  rename(
    Timestamp      = `Timestamp`,
    ObsTime        = `At what time did you observe the vehicles? (Please enter the time in 24-hour format, e.g., 14:30)`,
    VehicleType    = `Question: What type of vehicle did you observe?`,
    VehicleColor   = `What is the primary color of the vehicle?`,
    Comments       = `Do you have any additional comments or observations about this vehicle or the traffic conditions?`
  )

glimpse(latest_data)

names(logged_data)

# Step 3: Compute Summary Values
# Example summary 1: Total number of observations
total_obs <- nrow(latest_data)

total_obs

# Example summary 2: Frequency count of each vehicle type
vehicle_type_summary <- latest_data %>%
  group_by(VehicleType) %>%
  summarize(Count = n(), .groups = "drop")

vehicle_type_summary
# This Sums the total different types of vehicles

# Print summary values to the console
print(paste("Total Observations:", total_obs))
print(vehicle_type_summary)

# Step 4: Create Bar Charts using ggplot2

# Bar Chart 1: Frequency of Vehicle Types
plot_vehicle_type <- ggplot(latest_data, aes(x = VehicleType)) +
  geom_bar(fill = "#6a0dad") +
  labs(title = "Frequency of Vehicle Types",
       x = "Vehicle Type",
       y = "Count") +
  theme_minimal()

# Display the first bar chart
print(plot_vehicle_type)

# Bar Chart 2: Frequency of Vehicle Colors
plot_vehicle_color <- ggplot(latest_data, aes(x = VehicleColor)) +
  geom_bar(fill = "#B2C248") +
  labs(title = "Frequency of Vehicle Colors",
       x = "Vehicle Color",
       y = "Count") +
  theme_minimal()

# Display second bar chart
print(plot_vehicle_color)

```

The total number of vehicle observations is **`r total_obs`**.

# This shows the total amount of vehicles seen

The most frequently observed vehicle type is **`r paste(vehicle_type_summary$VehicleType[which.max(vehicle_type_summary$Count)], "with", max(vehicle_type_summary$Count), "observations")`**.

# This shows the most common vehicle type seen in my local area.
```{Rspacechunk2}

# ---------------------------------------------------------------------------
# FINAL CODE FOR REPORT:
# The code above calculates two summary values:
#   1. Total number of observations (total_obs)
#   2. vehicle type count (vehicle_type_summary)
#
# It also produces two informative bar charts:
#   - chart for the frequency of each vehicle type (plot_vehicle_type)
#   - chart for the frequency of vehicle colors (plot_vehicle_color)


```

